%-------------------------
% Resume in Latex
% Author : Jeffery
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
	\textbf{\Huge \scshape Jeffery Zhan} \\ \vspace{1pt}
	\small 289-300-1504 $|$ \href{mailto:jefferyzhan84@gmail.com}{\underline{jefferyzhan84@gmail.com}} $|$ 
	\href{https://linkedin.com/in/jeffery-zhan}{\underline{linkedin.com/in/jeffery-zhan}} $|$
	\href{https://github.com/jeffzhan}{\underline{github.com/jeffzhan}}
\end{center}
%---------------------------

%-----------EDUCATION-----------
\section{Education}
	\resumeSubHeadingListStart
		\resumeSubheading
		{University of Toronto}{Toronto, ON}
		{Bachelor of Science in Computer Science (Co-op)}{Expected: April 2025}
		\resumeItemListStart
			\resumeItem{\textbf{Courses:} Data Structures \& Algorithms, Software Design,  Computer Organization, Operating Systems, Systems Programming, Software Engineering}
			\resumeItem{\textbf{Awards/Activities:} UofT Scholar (\textbf{Top 5\%}), Art Studio, Gym \& Fitness Club, Innis College}
		\resumeItemListEnd
	\resumeSubHeadingListEnd
%-------------------------------

%-----------EXPERIENCE-----------
\section{Experience}
	\resumeSubHeadingListStart
	
		\resumeSubheading{Full-stack Developer Co-op}{May 2023 -- Dec 2023}{Temerity Analytics Inc.}{Toronto, ON}
		\resumeItemListStart\
  			\resumeItem{Built API integrations to platforms such as Google Analytics 3 and 4, TikTok Business, and Pinterest Business with \textbf{Django} and \textbf{PostgreSQL}, enabling clients to view and store up to \textbf{2 years} of historical data.}
			\resumeItem{Improved API response times  by \textbf{45\%} by leveraging query indexing, eager loading, and query profiling in \textbf{Django}.}
			\resumeItem{Revamped the main dashboard end-to-end using \textbf{Angular} and \textbf{Django} to provide \textbf{1.75x} more utility through aggregating and visualizing key marketing metrics, catering to industry needs and client feedback.}
			\resumeItem{Shortened onboarding duration by \textbf{8+ hours} by centralizing and updating \textbf{60 pages} of documentation on \textbf{Confluence}, as well as standardizing effective documentation practices on \textbf{Jira} and \textbf{GitHub}.}
		\resumeItemListEnd

		\resumeSubheading
		{Application Developer Intern}{May 2022 -- Aug 2022}
		{SR Research Ltd.}{Oakville, ON}
		\resumeItemListStart\
			\resumeItem{Streamlined company's operations efficiency by \textbf{50\%} and eliminated \textbf{$\sim$3} error-prone areas in the production pipeline by building a specialized full-stack IMS as the sole developer.}
			\resumeItem{Created a dashboard with \textbf{React} to manage inventory, generate purchase orders, and schedule restocking.}
			\resumeItem{Migrated over \textbf{150} product \& material entries into a \textbf{Django} and \textbf{MySQL} backend and designed flexible model schemas to accommodate business specifications and product variations.}
			\resumeItem{Developed an \textbf{R} program to quantify the curvature of eye movement paths using mathematical algorithms.}
		\resumeItemListEnd

	\resumeSubHeadingListEnd
%--------------------------------

%-----------PROJECTS-----------
\section{Projects}
	\resumeSubHeadingListStart
	
		\resumeProjectHeading{\textbf{\href{https://github.com/jeffzhan/UofT-Smart-Timetable-Generator}{UofT Smart Timetable Generator}} $|$ \emph{Java, JUnit}}{}
		\resumeItemListStart
			\resumeItem{Created a timetable generator that returns optimized, conflict-free schedules for a student's desired courses.}
			\resumeItem{Co-led a team of 8 developers, adhering to SOLID design principles with test-driven development in \textbf{Java}.}
			\resumeItem{Increased testing code coverage to \textbf{100\%} using \textbf{JUnit} and utilized SonarLint extensively to maintain code quality.}
			\resumeItem{Engineered tag \& filtering systems for more effective timetable searching, refining timetable options by \textbf{75\%}.}
		\resumeItemListEnd
		\resumeProjectHeading{\textbf{{Homes for Heroes (UofT Blueprint)}} $|$ \emph{React,  JavaScript, Express.js}}{}
		\resumeItemListStart
		\resumeItem{Centralized client management by building a full-stack app comprising of CRM, management, and survey tools.}
		\resumeItem{Constructed key UI components including login/signup, profile, and navigation, using \textbf{React} and \textbf{Material-UI}.}
		\resumeItem{Collaborated closely in a team of 8 within an \textbf{Agile} environment to ensure timely delivery of milestones.}
		\resumeItemListEnd
		\resumeProjectHeading
		{\textbf{\href{https://github.com/jeffzhan/civility}{Toxicity Measurer (Hack the North)}} $|$ \emph{Next.js, JavaScript, Express.js, Cohere API, Vercel}} {}
		\resumeItemListStart
			\resumeItem{Developed a full-stack application that conducts sentiment analysis to detect toxicity levels in text.}
			\resumeItem{Built a minimal and accessible UI/UX with \textbf{Next.js} and the \textbf{Material-UI} library.}
			\resumeItem{Integrated the \textbf{Cohere API} for NLP text classification in \textbf{Express.js}.}
			\resumeItem{Achieved deployment using \textbf{Vercel} and \textbf{Heroku} for the frontend and backend respectively.}
		\resumeItemListEnd
	\resumeSubHeadingListEnd
%------------------------------

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
			\textbf{Languages}{: Python, C, TypeScript/JavaScript, Bash, Java, SQL, HTML/CSS} \\
			\textbf{Frameworks/Libraries}{: Angular, React, Next.js, Django, Express.js, Node.js, Bootstrap, TailwindCSS} \\
			\textbf{Tools \& Utilities}{: PostgreSQL, Git, Docker, Postman, Agile, CI/CD,  Unix, Linux, Heroku, Jira, Confluence} \\
	}}
\end{itemize}
%--------------------------------------

%-----------EXTRACURRICULARS-----------
% \section{Extracurriculars}
% 	\resumeSubHeadingListStart
% 		\resumeProjectHeading
% 		{\textbf{Visual Artist}, UofT Anime \& Manga Assc.} {Sep 2021 -- Present}
% 		\resumeProjectHeading
% 		{\textbf{Gym-goer}, Athletic Centre} {Forever}
% 	\resumeSubHeadingListEnd
%-------------------------------------

\end{document}
